Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2020-04-15 referee PRD/RefereeResponse_DN12236.tex

\magnification=1050 \baselineskip=12pt plus 1pt minus 2pt
\nopagenumbers

\noindent {\bf Manuscript Code Number: DN12236}

\smallskip
\noindent {\bf Title: Scattering from compact objects: Regge poles and the Complex Angular Momentum method}

\smallskip
\noindent {\bf Authors: Mohamed Ould El Hadj, Tom Stratton and Sam R. Dolan}

\bigskip
\bigskip

We thank the referee for her/his careful reading of our manuscript and her/his useful remarks that have been taken into account and that have permitted us to improve our article:

\bigskip

\noindent $\underline{\hbox{Comments:}} $
\medskip

\bigskip
\qquad - In the case where $α \rightarrow0$, the effective potential becomes continuous and the branch of Regge poles associated with the discontinuity, i.e. the broad resonances ``disappears''. However, this does not mean that the black hole does not have a pole. Because the effective potential of the black hole is not only continuous, it has a maximum and the poles of the $\cal{S}$--matrix (QNFs and/or RPs) are associated with this maximum (see for example Folacci, Decanin and Jensen: Complex angular momentum in black hole physics and quasinormal modes and reference therein. Ref[40] in our article).

\bigskip
\qquad - Perhaps one can refer to the use of the approximation Eq.(30) and (31) of the function f(r). The WKB approximation  in this case is valid just for $R > 3M$ i.e. in case the potential has no well.

\bigskip
\qquad -  Usually we stop when the sum over the Regge poles converges. For the background integral, its evaluation allows us to see whether it is negligible or not. For example, in the case of the black hole and ultra-compact objects, in the high frequency regime, the background integral is negligible. This is surprising since this is not the case in other areas of physics (acoustics, optics, electromagnetics, quantum mechanics,...), where the CAM method finds its origins, and this independently of the frequency.

\bigskip\bigskip

\noindent $\underline{\hbox{Other changes:}}  $
\medskip

\smallskip
\qquad - Do not forget to add the Ref[Sebastian H. Völkel and Kostas D. Kokkotas] :  On the Inverse Spectrum Problem of Neutron Stars.

%@article{Volkel:2019gpq,
%      author         = "Völkel, Sebastian H. and Kokkotas, Kostas D.",
%      title          = "{On the Inverse Spectrum Problem of Neutron Stars}",
%      journal        = "Class. Quant. Grav.",
%      volume         = "36",
%      year           = "2019",
%      number         = "11",
%      pages          = "115002",
%      doi            = "10.1088/1361-6382/ab186e",
%      eprint         = "1901.11262",
%      archivePrefix  = "arXiv",
%      primaryClass   = "gr-qc",
%      SLACcitation   = "%%CITATION = ARXIV:1901.11262;%%"
%}

\vfill \eject \bye

### 2020-04-15 rainbowCAM.tex
made final changes for referee response

Here we follow the approach of Zhang, Wu and Leung~\cite{Zhang:2011pq}, who applied the WKB method to determine the axial \textit{w}-modes of a variety of stellar models. We adapt their method to obtain analytical approximations for the ``broad resonances'' for massless waves on a stellar background. The starting point is the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}). 
It is valid only for models with $R/M>3$.

@@

For any stellar model (such as a polytropic fluid sphere), the potential may in general be $C^{N}$ at the surface (and $C^{\infty}$ elsewhere). In this case, $\mathcal{R}$ and thus the broad resonance branch depends on the discontinuity in the $N$-th derivative of the potential at $r=R$. We do not go into detail here, but see Eq.~4.5 of Ref. \cite{Zhang:2011pq}.

@@

By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~(\ref{eq:alpha}), Eq.~(\ref{lambda_Approx}) and Fig.~\ref{fig:Veff}). Extending the WKB method to higher orders would improve the accuracy of this approximation, and further work is need to obtain asymptotic approximations for the surface-wave branch, and the narrow-resonance branch.

@@

In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely, and accelerating the convergence. This is a possible direction for a future investigation.

>>>>

Here we follow the approach of Zhang, Wu and Leung~\cite{Zhang:2011pq}, who applied the WKB method to determine the axial \textit{w}-modes of a variety of stellar models (see also \cite{Volkel:2019gpq}). We adapt their method to obtain analytical approximations for the ``broad resonances'' for massless waves on a stellar background. The starting point is the radial equation (\ref{H_Radial_equation}) with either the effective potential for the scalar field (\ref{Inside_Potentiel}), or for axial gravitational perturbations (\ref{RW_Potentiel_axialGW}). 
It is valid only for models with $R/M>3$.

@@

For any stellar model (such as a polytropic fluid sphere), the potential may in general be $C^{N}$ at the surface (and $C^{\infty}$ elsewhere). In this case, $\mathcal{R}$ and thus the broad resonance branch depends on the discontinuity in the $N$-th derivative of the potential at $r=R$. We do not go into detail here, but see Eq.~4.5 of Ref. \cite{Zhang:2011pq}. 
Recall that the above analysis is not appropriate for compact bodies with $R/M<3$ and black holes (since the effective potential has a qualitatively different structure, and the ansatz Eq.~(\ref{Approx_infinity}) is not valid ).

@@

By applying a WKB method at lowest order, we have obtained a better understanding of the spectrum of the broad resonances, finding that the magnitude of the imaginary part is linked to the magnitude of the discontinuity in the effective potential at the surface of the body (see Eq.~(\ref{eq:alpha}), Eq.~(\ref{lambda_Approx}) and Fig.~\ref{fig:Veff}). Extending the WKB method to higher orders would improve the accuracy of this approximation, and further work is needed to obtain asymptotic approximations for the surface-wave branch, and the narrow-resonance branch.

@@

Here we have numerically determined if a background integral, and how many Regge-poles and residues, need to be calculated to accurately reproduce a scattering cross section in an angular region. Loosely speaking, for scattering at higher frequencies, more poles must be included since there are more broad resonances. Also the background integral is negligible except for weak glory scattering. This is an interesting result in itself (as noted in \cite{Folacci:2019cmc,Folacci:2019vtt}) since in most CAM scattering studies the background integral is significant in geometrically illuminated regions \cite{Nussenzveig:2006}. 
\tom{Speculatively, this could be related to the long range nature of gravitational scattering by compact bodies (it is not just the body that is scattering, but the bodies extended gravitational field). By contrast, in acoustics, quantum mechanics, and optics [\emph{find citations}] the scatterer generally has a short range influence.} 
An asymptotic analysis is an important next step towards understanding the role of the background integral and higher Regge-pole overtones, both computationally and, in a semiclassical interpretation, physically.

In the case of Mie scattering, a powerful extension of the CAM approach is to define the so-called Regge-Debye poles using the Debye expansion (see the chapter 9 of the monograph of Nussenzveig \cite{Nussenzveig:2006}), thereby eliminating the broad resonance branch entirely, and accelerating the convergence. This is another possible direction for a future investigation.
